\documentclass[a4paper]{simplecv}

\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{hyperref}
\usepackage{color}

\usepackage{natbib}
%\bibpunct{(}{)}{;}{a}{,}{,}
%\usepackage[fixlanguage]{babelbib}
%\selectbiblanguage{english}

\parindent0pt

\textwidth14.5cm
\oddsidemargin1.3cm

\def\FormatName#1{%
  \def\myname{Gero Walter}%
  \edef\name{#1}%
  \ifx\name\myname
    \textbf{#1}%
  \else
    #1%
  \fi
}



\begin{document}

\pagestyle{myheadings}
%\markright{Gero Walter, Department of Industrial Engineering \& Innovation Sciences, TU Eindhoven \hfill}
\markright{Dr.\ rer.\ nat.\ Gero Walter, Dipl.-Statistician \hfill}


%\leftheader{
%Institut f?r Statistik\\
%Ludwig-Maximilians-Universit?t M?nchen\\
%Tel: +49 89 2180 3698
%}

%\rightheader{
%\url{Gero.Walter@stat.uni-muenchen.de}\\
%\url{www.stat.uni-muenchen.de/~walter}
%\texttt{\small Gero.Walter@stat.uni-muenchen.de}\\
%\texttt{\small www.stat.uni-muenchen.de/\,$\tilde{}\;$walter}
%}

\title{Curriculum Vitae}
\nocite{itip-statinf,Troffaes2014a,diss,Walter2012b,Troffaes2012a,Walter2011a,Walter2010a,%
Walter2009b,Walter2009a,Walter2007c,Walter2007b,Walter2007a,Walter2006a}

\vspace*{-10ex}
\maketitle

\textbf{\large Dr.\ rer.\ nat.\ Gero Walter, Dipl.-Statistician}\\[2ex]
%***\url{http://www.stat.uni-muenchen.de/~walter}\\
\url{mailto:g.m.walter@tue.nl}\\
\url{mailto:gero@gmx.at}\\
%Tel: +49 89 2180 3925\\
%Tel: +44 781 891 77 83 (English mobile)\\
Tel: +49 174 639 56 13 (German mobile)\\
Tel: +31 638 377 678 (Dutch mobile)\\

Born June 26th, 1979 in T\"{u}bingen, Germany. Unmarried.
%Parents: Bernhard Walter, Christa Walter nee Wend.\\%[1ex]
%Sister Simone, born 1976; brother Jan, born 1981.\\%[1ex]
%Marital status: unmarried.

%\vspace*{-2ex}
\section{CV in a nutshell}
\begin{topic}
\item[\bfseries 2015] Postdoctoral Researcher at TU Eindhoven (NL),
independent research and Master thesis project supervision in reliability and maintenance planning.
\item[\bfseries 2014] Temporary Lecturer at Durham University (UK),
teaching courses in Bayesian statistics and decision theory.
\item[\bfseries 2013] Dr.\ rer.\ nat.\ (PhD) in Statistics at LMU Munich (DE),
thesis on Bayesian methods using sets of prior distributions.
\item[\bfseries 2007] Diplom-Statistiker at LMU Munich (DE),
thesis on Bayesian linear regression under limited information.
\end{topic}


\section{CV details}
%\textbf{\sf Current status and affiliation} \dotfill \pageref{current}\\
%\textbf{\sf Awards} \dotfill \pageref{awards}\\
\textbf{\sf Education and work experience} \dotfill \pageref{education}\\
\textbf{\sf Student project supervision} \dotfill \pageref{supervision}\\
\textbf{\sf Teaching} \dotfill \pageref{teaching}\\
\textbf{\sf Talks and Posters} \dotfill \pageref{talks}\\
\textbf{\sf Other scientific activities} \dotfill \pageref{other}\\
\textbf{\sf Languages} \dotfill \pageref{languages}\\
\textbf{\sf List of publications} \dotfill \pageref{publications}\\


%\section{Current status and affiliation}
%\label{current}
%Research interests (see also List of publications, page~\pageref{publications}):
%\begin{itemize}
%\item Statistical methods in reliability and maintenance
%\item Generalised Bayesian approaches based on imprecise probabilities
%\item Modelling of prior-data conflict
%\item Imprecise probability models for linear and generalised linear regression
%%\item Bayesian variable selection %(spike-and-slab priors, \ldots)
%\item Statistical methods in epidemiology
%\end{itemize}

\section{Awards}
\label{awards}
\begin{topic}
\item[07 / 2015] Best poster award (1st Prize) at ISIPTA'15\\
                 (joint work with Frank Coolen and Simme Douwe Flapper).
\item[07 / 2015] Best poster award (2nd Prize) at ISIPTA'15\\
                 (joint work with Christoph Jansen and Thomas Augustin).
\item[07 / 2011] IJAR Young Researcher Award 2011 (Silver Award).
\item[07 / 2011] Best poster award (1st Prize) at ISIPTA'11\\
                 (joint work with Manuel Eugster and Thomas Augustin).
\end{topic}


\newpage
\section{Education and work experience}
\label{education}

%\subsection{Studies including work experience and responsibilities}

\begin{topic}
\item[\hspace*{-2ex}\bfseries since 2 / 2015] Postdoctoral Researcher
                  at the Operations, Planning, Accounting, and Control (OPAC) group,
                  Department of Industrial Engineering \& Innovation Sciences,
                  TU Eindhoven, NL.
DINALOG project ``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).

\item[\hspace*{-2ex}\bfseries 1 -- 12 / 2014]Temporary Lecturer
                  at the Department of Mathematical Sciences,
                  Durham University, Durham, UK,
                  teaching lectures on Bayesian Statistics and Decision Theory,
                  and supervising final year projects. 


\item[\hspace*{-2ex}\bfseries 10 / 2013] Ph.D.\ in Statistics (magna cum laude) at
                  Lud\-wig-Maximi\-li\-ans-Uni\-ver\-si\-ty (LMU) Munich, Germany,
                  with thesis ``Generalized Bayesian Inference under Prior-Data Conflict''
                  (\cite{diss} in the List of publications, page~\pageref{publications}).


\item[\hspace*{-2ex}\bfseries 2007 -- 2013] Research Assistant at the Working Group `Methodological Foundations of Statistics and their Applications'
                    (head Prof.\ Dr.\ Thomas Augustin),
                    Department of Statistics, LMU Munich, Germany.
                    Responsibilities included teaching for statistics students and other majors, %postgraduate ???
                    assistance in supervision of Bachelor's theses,
                    administrative work and student guidance related to the department's Bachelor's and Master's study programmes.
%                    Responsibilities assumed at the Department of Statistics:
%\begin{itemize}
%\item Teaching in courses for students in Statistics and other majors\\ (see `Teaching', page~\pageref{teaching}).
%\item Assistance in supervision of Bachelor's theses.
%\item Student guidance concerning the Bachelor's and Master's study programmes.
%\item Administrative work related with the Bachelor's and Master's study programmes.
%\end{itemize}

\item[7 / 2010] Participant of the \emph{4th SIPTA School on Imprecise Probabilities}, Durham. %, UK.

\item[7 / 2008] Participant of the \emph{3rd SIPTA School on Imprecise Probabilities}, Montpellier. %, France.

\item[\hspace*{-2ex}\bfseries 2000 -- 2007] Student in the Statistics study programme %of study  
(\emph{Di\-plom-Studiengang Statistik}, equivalent to an integrated Master's programme) % of study)
at LMU Munich,
with `subjects of application' Political Science and Sociology;
%
\emph{Diplom} (equivalent to a Master's degree) with cumulative grade 1.37
(1 = `very good', best grade; 2 = `good'), including a thesis
with grade 1.0 (best grade) %(`very good', best grade)
%Diploma thesis (equivalent to a Master's thesis)
on the generalization of Bayesian estimation of regression coefficients using sets of priors
(in German, ``Bayes-Regression mit Mengen von Prioris - Ein Beitrag zur Statistik unter komplexer Unsicherheit'',
see \cite{Walter2006a} in the list of publications on page~\pageref{publications}),
supervised by Prof.\ Dr.\ Thomas Augustin.

\item[2005 -- 2007] Project work for HelmholzZentrum Research Unit ``Epidemiology of Air Pollution Health Effects'' (see below).

\item[7 -- 9 / 2005] Internship at HelmholzZentrum M\"unchen -- German Research Center for Environmental Health (formerly GSF),
Institute for Epidemiology, Research Unit `Epidemiology of Air Pollution Health Effects' (head Dr.\ A.\ Peters);
working for the AIRGENE study group.

\item[2003 -- 2007] Student assistant at the Department of Statistics, Ludwig-Maximi\-li\-ans-Uni\-ver\-si\-ty Munich,
working for Prof.\ Dr.\ Thomas Augustin.

\item[2003] Elected as student representative in the council of the faculty for Mathematics, Informatics and Statistics; reelected in 2004.

\item[2002 -- 2003] Guest student at the University of Palermo, Italy, with the Erasmus programme (one year). %Two semester

\item[2001 -- 2007] Active member of the student council of the department (`Fachschaft'),
co-organizing support for first-year students, German-wide meetings of statistics students, and several festivities.

%\item[1990 -- 1999] Secondary School (Eugen-Bolz-Gymnasium) in Rottenburg am Neckar.
%\item[1986 -- 1990] Primary school (Hohenberg-Grundschule) in Rottenburg am Ne\-ckar.
\end{topic}


\section{Student project supervision}
\label{supervision}

\begin{itemize}
\item Master thesis Robin van Sprang (TU Eindhoven),
in collaboration with Marel Poultry Processing (condition-based maintenance, ongoing)
\item Master thesis Tom Aventuur (TU Eindhoven),
in collaboration with Tata Steel (maintenance planning, ongoing).
\item Master thesis Wouter Lubbers (TU Eindhoven),
in collaboration with Tata Steel Packaging (condition-based maintenance, 2016).
\item Master thesis Lex Roording (TU Eindhoven),
in collaboration with DAF Trucks (reliability assessments, 2016).
\item Master thesis Ren\'{e} Gorisse (TU Eindhoven),
in collaboration with BP Refinery Rotterdam (maintenance planning, 2016).
\item Master thesis Robin Bakker (TU Eindhoven),
in collaboration with Smurfit Kappa Roermond Papier (maintenance planning, 2016).
\item Bachelor thesis Tijs Metink (TU Eindhoven),
in collaboration with the Royal Netherlands Navy (degradation process and life cycle analysis, 2016).
\item Bachelor thesis Stefan van der Linden (TU Eindhoven),
in collaboration with FEI (spare parts planning, 2016).
\item Master thesis Lisanne Derks (TU Eindhoven),
in collaboration with FrieslandCampina (promotional sales prediction, 2015).
\item Master thesis Arjen Schr\"{o}der (TU Eindhoven),
in collaboration with NedTrain and Frankfurt Consulting Engineers (condition-based maintenance, 2015).
\item Master thesis Steef Pepping (TU Eindhoven),
in collaboration with Stork (human errors in maintenance, 2015).
\item Master thesis Anouk Geleen (TU Eindhoven),
in collaboration with SABIC (maintenance planning, 2015).
\item Bachelor thesis Ruud Meijering (TU Eindhoven),
in collaboration with VDL Industrial Modules (quality control, 2015).
\item Final year project Andrew Graham (Durham University, reliability analysis, 2015).
\item Bachelor thesis Norbert Krautenbacher (LMU Munich, generalized Bayesian methods, 2011)
\end{itemize}


%\vspace*{-8ex}
\section{Teaching}
\label{teaching}
%\vspace*{-1.5ex}
Teaching material is available upon request;
teaching material for some of the courses at LMU (in German) can also be downloaded from the respective course homepages
linked from \url{http://www.statistik.lmu.de/~walter/lehre_en.html}.
%\vspace*{-0.5ex}
\begin{topic}
\item[August 2016] Lectures and tutorials on robust Bayesian statistics, Bayesian hierarchical modelling, Simulation and MCMC
(\emph{7th SIPTA summer school}, Durham University, UK)
\item[December\,2015] Lecture and tutorial on Bayesian statistics and prior-data conflict (Lund University, SE) 
\item[Michaelm.2014] Lectures for ``Decision Theory''

                    Tutorials for ``Probability and Actuarial Mathematics'' (Dr.\ Ostap Hryniv)

                    Tutorials for ``Probability and Geometric Topology'' (Dr.\ Ostap Hryniv)

\item[Epiphany 2014] Lectures for ``Bayesian Statistics''

                    Tutorials for ``Calculus and Probability I'' (Dr.\ Matthias Troffaes)

                    Computer classes for ``Statistics I'' (Dr.\ Peter Craig) 

\item[Summer 2012]  Support classes for ``Statistics 2 for sociologists'' (Prof.\ Dr.\ Helmut K\"{u}chenhoff)

\item[Winter 11/12] Support classes for ``Statistics 1 for sociologists'' (Prof.\ Dr.\ Gernot M\"{u}ller)

                    Seminar ``Insights into current research topics in statistics''\\ (Prof.\ Dr.\ Thomas Augustin)
                    
\item[Summer 2011]  Support classes for ``Statistics 2 for sociologists'' (Prof.\ Dr.\ Ulrich P\"{o}tter)

\item[Winter 10/11] Support classes for ``Introduction to Bayesian statistics''\\ (Prof.\ Dr.\ Helga Wagner)

                    Support classes for ``Statistics 1 for sociologists'' (Prof.\ Dr.\ Helga Wagner)

                    Additional exercise classes for ``Statistics 1 for sociologists''\\ (Prof.\ Dr.\ Helga Wagner)

                    Seminar ``Statistical challenges in social surveys''\\ (Prof.\ Dr.\ Thomas Augustin, PD Dr.\ Rudolf Seising)

\item[Summer 2010]  Support classes for ``Decision Theory'' (Prof.\ Dr.\ Thomas Augustin)

                    Support classes for ``Statistics 2 for sociologists''\\ (Prof.\ Dr.\ Thomas Augustin)

\item[Winter 09/10] Support classes for ``Statistics 1 for sociologists''\\ (Prof.\ Dr.\ Thomas Augustin)

                    Additional exercise classes for ``Statistics 1 for sociologists''\\ (Prof.\ Dr.\ Thomas Augustin)

                    Seminar ``Philosophies of Science and Transformations of Knowledge in the 20th century -- an interdisciplinary Seminar on the Foundations of Statistics''
                    (Prof.\ Dr.\ Thomas Augustin, Prof.\ PD Dr.\ Rudolf Seising)

\item[Summer 2009]  Support classes for ``Decision Theory'' (Prof.\ Dr.\ Thomas Augustin)

                    Support classes for ``Statistics 2 for sociologists'' (Dr.\ Carolin Strobl)

\item[Winter 08/09] Support classes for ``Statistics 1 for sociologists'' (Dr.\ Carolin Strobl)

                    Support classes for ``Statistics 1 for economists and business economists'' (PD.\ Dr.\ Christian Heumann)

\item[Summer 2008]  Support classes for ``Decision Theory'' (Prof.\ Dr.\ Thomas Augustin)

                    Support classes for ``Statistics 2 for economists and business economists'' (Prof.\ Dr.\ Helge Toutenburg)

\item[Winter 07/08] Support classes for ``Statistics 3 for students with Statistics as a minor/elective subject'' (Prof.\ Dr.\ Ludwig Fahrmeir)

                    Support classes for ``Statistics 1 for economists and business economists'' (Prof.\ Dr.\ Helge Toutenburg)

                    Support classes ``Discussion of selected works on methodological basics of Statistics and its applications''

\item[Summer 2007]  Seminar ``Modelling of \emph{uncertain knowledge} -- Alternatives to and generalizations of the concept of probability'' (Prof.\ Dr.\ Thomas Augustin)
\end{topic}


\section{Talks and Posters}
\label{talks}

Talk slides and posters can be downloaded from \url{http://www.statistik.lmu.de/~walter/forschung_en.html#talks}.

\begin{topic}
\item[11 / 2014] ``Cautious Uncertainty Modelling in Common-Cause Failure Models with Sets of Conjugate Priors'', talk at
                 the Department of Industrial Engineering \& Innovation Sciences, TU Eindhoven, the Netherlands.
\item[09 / 2014] ``Sample Size Calculations based on Posterior Imprecision'', talk at
                 \emph{Seventh Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://users.ugent.be/~slopatat/wpmsiip2014/index.html}{WPMSIIP 7})},
                 Ghent University, Belgium.

\item[06 / 2014] ``Density Ratio Class Models and Imprecision'',
                 talk at the Statistics Department of LMU Munich, Germany.

\item[10 / 2013] ``Generalized Bayesian Inference under Prior-Data Conflict'', Ph.D.\ defense talk at
                 the Statistics Department of LMU Munich, Germany.

\item[09 / 2013] ``Prior-Data Conflict in Generalized Bayesian Inference'', talk at
                 the Department of Mathematical Sciences, Durham University, UK.

\item[03 / 2013] ``Modelling Epistemic Uncertainty in Common-Cause Failure Models with Sets of Conjugate Priors''
                 (joint work with Matthias Troffaes and Dana Kelly), talk at
                 \emph{First workshop on Uncertainty Quantification and Data Assimilation in Numerical Simulation of Physical Systems
                 for Risk-Informed Decision Making (\href{http://www.maths.dur.ac.uk/users/matthias.troffaes/simride2013/}{SIMRIDE 2013})}, Durham University, UK.

\item[03 / 2013] ``Bayesian Inference with Sets of Conjugate Priors: Parameter Set Shapes and Model Behaviour'', talk at the
                 \emph{Statistics Seminar} of the Department of Mathematical Sciences, Durham University, UK.

\item[09 / 2012] ``Boat or bullet: prior parameter set shapes and posterior imprecision'', talk at
                 \emph{Fifth Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://statsoz-neu.userweb.mwn.de/research/WPMSIIP_2012/}{WPMSIIP 5})},
                 LMU Munich, Germany.

\item[06 / 2012] ``Bayesian Inference with Sets of Conjugate Priors'', talk at \emph{Sommerklausur 2012} of the department's graduate school
                 ``Statistics: Theory and Methods of Empirical Modeling'', Herrsching, Germany.

\item[11 / 2011] ``Sets of canonical parameters in imprecise Bayesian inference with conjugate priors,'', talk at
                 \emph{Workshop on Geometry of Imprecise Probability and related Statistical Methods (\href{http://maths.dur.ac.uk/stats/people/fc/geomip11.html}{GEOMIP-11})}, Durham University, UK.

\item[09 / 2011] ``Regression Models in Statistics --- A Short Guide Through a Set of Abbreviations Containing the Letters L, M, G, and A'',
                 ``Imprecise Bayesian Linear Regression'', and "A New Class of Parameter Shapes for Generalized iLUCK Models",
                 three talks at the
                 \emph{Fourth Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://wpmsiip2011.fdvinfo.net/c/646/Information/}{WPMSIIP 4})},
                 University of Ljubljana, Slovenia.

\item[07 / 2011] ``A Network Analysis of the Imprecise Probability Community based on ISIPTA Electronic Proceedings''
                 (joint work with Manuel Eugster and Thomas Augustin),
                 poster at \emph{\href{http://www.sipta.org/isipta11/}{ISIPTA '11}}, University of Innsbruck, Austria (see `Awards' and `Software').

\item[07 / 2011] ``On Prior-Data Conflict in Predictive Bernoulli Inferences'' (joint work with Frank Coolen and Thomas Augustin),
                 talk and poster at \emph{\href{http://www.sipta.org/isipta11/}{ISIPTA '11}}, University of Innsbruck, Austria.

\item[09 / 2010] ``Prior-Data Conflict: a brief introduction'' and ``Software for Generalized iLUCK-models'', two talks at the
                 \emph{Third Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://www.maths.dur.ac.uk/users/matthias.troffaes/wpmsiip2010/}{WPMSIIP 3})},
                 Durham University, UK.

\item[05 / 2010] ``\emph{Strong happiness} and other properties of certain imprecise probability models when treating samples sequentially'',
                 talk at the Statistics Department of LMU Munich, Germany.

\item[04 / 2010] ``The Effect of Prior-Data Conflict in Bayesian Linear Regression'', talk at the
                 \emph{Lecture Day with Prof. Balakrishnan}, Durham University, UK.

\item[03 / 2010] ``Prior-Data Conflict and Generalized Bayesian Inference'' (extended version of talk below), talk at the
                 \emph{Statistics Seminar} of the Department of Mathematical Sciences, Durham University, UK.

\item[03 / 2010] ``Prior-Data Conflict and Generalized Bayesian Inference'', talk at
                 \emph{\href{http://www.statistik.tu-dortmund.de/DAGStat2010/en/index.html}{DAGStat 2010}}, Dortmund, Germany.

\item[09 / 2009] ``Linear regression with sets of conjugate priors'', talk at the
                 \emph{Second Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://www.stat.uni-muenchen.de/~walter/workshop0909/}{WPMSIIP 2})}, LMU Munich, Germany.

\item[07 / 2009] ``Software for Generalized Bayesian Inference -- An object-oriented \textbf{R} implementation of generalized iLUCK-models'', poster at
                 \emph{\href{http://www.sipta.org/isipta09/}{ISIPTA '09}}, Durham University, UK.

\item[06 / 2009] ``Generalized iLUCK-models and prior-data conflict -- A contribution to Generalized Bayesian Inference'', talk at the
                 \emph{Young Researchers' Workshop of Deutsche Statistische Gesellschaft}, Merseburg, Germany.

\item[02 / 2009] ``Software for Generalized Bayesian Inference for Samples from Exponential Families -- An object-oriented \textbf{R} implementation of generalized iLUCK-models'', talk at
                 the Statistics Department of LMU Munich, Germany.

\item[05 / 2008] ``Generalized Bayesian Inference and Prior-data Conflict'' and ``Bayesian Estimation of Linear Regression Parameters with Sets of Conjugate Priors'', two talks at the
                 \emph{First Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://www.maths.dur.ac.uk/users/matthias.troffaes/workshopip2008/index.html}{WPMSIIP 1})}, Durham University, UK.

\item[12 / 2007] ``Imprecise probability models and prior-data conflict'', talk at
                 the Statistics Department of LMU Munich, Germany.

\item[07 / 2007] ``Linear Regression Analysis under Sets of Conjugate Priors'', talk and poster at
                 \emph{\href{http://www.sipta.org/isipta07/}{ISIPTA '07}}, Charles University, Prague, Czech Republic.

\end{topic}



%\newpage

\section{Other scientific activities}
\label{other}

\subsection{Research stays}
%\vspace*{-1.3ex}
\begin{topic}
\item[03 / 2013] Visiting researcher at the Department of Mathematical Sciences, Durham University, UK,
                 by invitation of Frank Coolen (2 weeks).
\item[11 / 2011] Visiting researcher at the Department of Mathematical Sciences, Durham University, UK,
                 by invitation of Frank Coolen (one week).
\item[02 -- 04 / 2010] Visiting researcher at the Department of Mathematical Sciences, Durham University, UK,
                 by invitation of Frank Coolen (2 months).
\end{topic}

%\newpage
\subsection{Software}

\begin{topic}
\item[08 / 2013] \texttt{luck}: Software for generalized Bayesian Inference with iLUCK-models (joint work with Norbert Krautenbacher),
                 add-on package for the statistical programming environment \textbf{R}. In development, project page
                 \url{http://r-forge.r-project.org/projects/luck/}.
                 Install from within \textbf{R} by\\ \texttt{install.packages("luck", repos="http://R-Forge.R-project.org")}
\item[06 / 2011] \texttt{ISIPTA}: Network Analysis of the Imprecise Probability Community based on ISIPTA Electronic Proceedings
                 (joint work with Manuel Eugster and Thomas Augustin, see `Awards' and `Talks and Posters'),
                 add-on package for the statistical programming environment \textbf{R} (\url{http://cran.r-project.org/package=ISIPTA}).
\end{topic}


%\vspace*{-0.5ex}
\subsection{Refereeing}
%\vspace*{-1.3ex}
%\begin{topic}
%\item[04 / 2011] Review for \emph{Biometrical Journal}.
%\item[07 / 2010] Review for \emph{International Journal of Approximate Reasoning}.
%\item[10 / 2009] Book Review for Elsevier, together with Thomas Augustin and Andrea Wiencierz.
%\item[01 / 2008] Review for \emph{Journal of Statistical Theory and Practice: Special Issue on Imprecision}.
%\end{topic}
\begin{topic}
\item[2008 -- 2015] Article reviews for
\emph{Journal of Statistical Theory and Practice},
\emph{International Journal of Approximate Reasoning},
\emph{Biometrical Journal}, and
\emph{ISIPTA} conference proceedings.

\item[2009] Book review for \emph{Elsevier}, together with Thomas Augustin and Andrea Wiencierz.
\end{topic}

\subsection{Workshop organisation}

%Links to the respective workshop homepages are provided at \url{http://www.statistik.lmu.de/~walter/forschung_en.html#other}.

\begin{topic}
\item[09 / 2012] Co-organisation of the \emph{Fifth Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://www.statistik.lmu.de/institut/ag/statsoz_neu/research/WPMSIIP_2012/}{WPMSIIP 5})}
                 at the Department of Statistics, Ludwig-Maximilians-University Munich (LMU),
                 together with Thomas Augustin, Marco Cattaneo, Georg Schollmeyer, and Andrea Wiencierz.
                 
\item[09 / 2011] Co-organisation of the \emph{Forth Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://wpmsiip2011.fdvinfo.net/c/646/Information/}{WPMSIIP 4})}
                 at the Faculty of Social Sciences, University of Ljubljana,
                 together with Damjan \v{S}kulj, Thomas Augustin, Frank Coolen, Gert de Cooman, and Matthias Troffaes.

\item[09 / 2010] Co-organisation of the \emph{Third Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://www.maths.dur.ac.uk/users/matthias.troffaes/wpmsiip2010/}{WPMSIIP 3})}
                 at the Department of Mathematical Sciences, Durham University,
                 together with Thomas Augustin, Frank Coolen, Richard Crossman, Nathan Huntley, and Matthias Troffaes.

\item[09 / 2009] Co-organisation of the \emph{Second Workshop on Principles and Methods of Statistical Inference with Interval Probability (\href{http://www.stat.uni-muenchen.de/~walter/workshop0909/}{WPMSIIP 2})}
                 at the Department of Statistics, Ludwig-Maximilians-University Munich (LMU),
                 together with Thomas Augustin, Marco Cattaneo, and Andrea Wiencierz.
\end{topic}

\subsection{Chairing}

\begin{topic}
\item[09 / 2014] Chair of the session on classification,
                 as part of \emph{\href{http://users.ugent.be/~slopatat/wpmsiip2014/index.html}{WPMSIIP 7}}.
%                 as part of the \emph{Seventh Workshop on Principles and Methods of Statistical Inference with Interval Probability (WPMSIIP 7)}
%                 at the SYSTeMS research group, Ghent University.

\item[09 / 2012] Co-chair of the sessions on classification, regression and support vector machines, together with Lev Utkin,
                 as part of \emph{\href{http://www.statistik.lmu.de/institut/ag/statsoz_neu/research/WPMSIIP_2012/}{WPMSIIP 5}}.
%                 as part of the \emph{Fifth Workshop on Principles and Methods of Statistical Inference with Interval Probability (WPMSIIP 5)}
%                 at the Department of Statistics, LMU Munich.

\item[09 / 2011] Co-chair of the session on modelling dependence / multivariate statistics, together with Alessio Benavoli,
                 as part of \emph{\href{http://wpmsiip2011.fdvinfo.net/c/646/Information/}{WPMSIIP 4}}.
%                 as part of the \emph{Forth Workshop on Principles and Methods of Statistical Inference with Interval Probability (WPMSIIP 4)}
%                 at the Faculty of Social Sciences, University of Ljubljana.

\item[09 / 2010] Chair of the session on prior-data conflict,
                 as part of \emph{\href{http://www.maths.dur.ac.uk/users/matthias.troffaes/wpmsiip2010/}{WPMSIIP 3}}.
%                 as part of the \emph{Third Workshop on Principles and Methods of Statistical Inference with Interval Probability (WPMSIIP 3)}
%                 at the Department of Mathematical Sciences, Durham University.

\item[09 / 2009] Co-chair of the session on regression, together with Jochen Einbeck,
                 as part of \emph{\href{http://www.stat.uni-muenchen.de/~walter/workshop0909/}{WPMSIIP 2}}.
%                 as part of the \emph{Second Workshop on Principles and Methods of Statistical Inference with Interval Probability (WPMSIIP 2)}
%                 at the Department of Statistics, Ludwig-Maximilians University Munich (LMU).

\item[05 / 2008] Co-chair of the session on regression, together with Jochen Einbeck,
                 as part of \emph{\href{http://www.maths.dur.ac.uk/users/matthias.troffaes/workshopip2008/index.html}{WPMSIIP 1}}.
%                 as part of the \emph{First Workshop on Principles and Methods of Statistical Inference with Interval Probability (WPMSIIP 1)}
%                 at the Department of Mathematical Sciences, Durham University.
\end{topic}


%\vspace*{-2.5ex}
%\subsection{Languages}
\section{Languages}
\label{languages}
%\vspace*{-1.3ex}
%\vspace*{-1ex}
\begin{tabular}{llllll}%
{\sf \emph{German}}    & mother tongue \qquad\qquad &
{\sf \emph{Italian}}   & fluently \qquad\qquad\qquad &
{\sf \emph{Icelandic}} & intermediate \\
{\sf \emph{English}}   & fluently &
{\sf \emph{French}}    & intermediate &
%{\sf \emph{Portuguese}} & basic
\end{tabular}
%
\iffalse
\begin{topic}
\item[German] mother tongue
\vspace*{-1ex}
\item[English] fluently
\vspace*{-1ex}
\item[Italian] fluently
\vspace*{-1ex}
\item[French] intermediate
\vspace*{-1ex}
\item[Icelandic] basic
\end{topic}
\fi


%\newpage

%\section{List of publications}
%\vspace*{-2.4ex}%

\bibliographystyle{unsrt}
%\bibliographystyle{myunsrt} %"Package natbib error: Bibliography not compatible with author-year citations." can be ignored

\renewcommand\refname{List of publications}
\label{publications}
\bibliography{eigene-bold}
%
%\begin{picture}
%\put(0,0){ABC}
%\end{picture
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace*{-14.1cm}%
%{\color{white}\rule{12ex}{2.2ex}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\rule{12ex}{2.2ex}

\end{document}
